---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# TestWithRStudio for Testing your R Package with RStudio in Continuous Integration
    
[![Travis-CI Build Status](https://travis-ci.org/Non-Contradiction/TestWithRStudio.svg?branch=master)](https://travis-ci.org/Non-Contradiction/TestWithRStudio)

## Why do we need `TestWithRStudio`?

As an R package developer, have you met the situation that your package
passes `R CMD check` but crashes RStudio?
`TestWithRStudio` can help you deal with this situation by testing your R package with
RStudio using continuous integration like Travis CI.

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Installation

You can get `TestWithRStudio` by
```{r eval=FALSE}
devtools::install_github("Non-Contradiction/TestWithRStudio")
```

## Basic Usage
```{r}
library(TestWithRStudio)

check_rstudio()

detailed_check_in_rstudio("1")

detailed_check_in_rstudio("q()")

detailed_check_in_rstudio("stop('This is an error!!')")

detailed_check_in_rstudio("doesntexist()")

detailed_check_in_rstudio("library(TestWithRStudio); crash()")
```

## TestWithRStudio for R Package Developers

## Suggestion and Issue Reporting

`TestWithRStudio` is under active development now.
Any suggestion or issue reporting is welcome!
You may report it using the link: <https://github.com/Non-Contradiction/TestWithRStudio/issues/new>.
Or email me at <lch34677@gmail.com> or <cxl508@psu.edu>.







